\section{Preparation Plan}
\label{sec:plan}

\begin{itemize}

\item Jan 23: Cylon on AWS Proposal and initial formulation of Qualification committee.  Began work on UCC/UCX 
\item March 23: Presented Cylon and AWS Work to Professor Yue Cheng's Data science 5110 class during a lecture
\item April 23: Received funding attached to NSF grant to use AWS. Applied for AWS Research grant
\item September 23: Applied UCC/UCX work to bare metal Rivanna to conduct derivative experiments
\item October 23: Received 30k grant from AWS
\item June 23: Successfully executed Cylon experiments on AWS Fargate
\item September 23: Began work integrating NAT Traversal in UCX/UCC
\item February 24: Presented Cylon and AWS Work to Professor Judy Fox's Data science 5110 class during a lecture
\item May 24:  Based on challenges and hurdles implementing Nat Traversal (TCP Hole Punching) in the UCX TCP transport, pivoted to recreating the FMI library as a custom AWS Lambda runtime for future integration into Cylon as a communicator.  This validated the NAT Holepunching capability as a viable option for high-performance communication in AWS Lambda.
\item June 24: Presented Serverless Cylon architecture and subset of work during WOSCx3 Serverless Computing Conference
\item September 24: Built Cylon UCC/UCX Singularity container, allowing derivative experiments across HPC and Clouds.  Developed Qualification exam abstract.
\item October 24: Reran experiments reconfigured for Lambda experiments and also to address error rates.  Discovered changes to the AWS Fargate stack that prevented executing of Cylon using UCX.  This third round of experiments excluded AWS Fargate for this reason.
\item December 24: Contributed FMI work for the Cloud-based Astronomy Framework (CAI).  Demonstrated the use of FMI and the use of AWS Lambda as a critical impact of cost.  Detailed experiments using collective operations to provide summation across multiple running lambda function.
\item January 25: Completed draft for Qualification Report Paper and developed proposal presentation
\item February 25: Qualification Exam Proposal
\end{itemize}